Value Ordering, Discrepancies, and Restarts for Subgraph Algorithms

### 2018-04-16 paper/paper.tex
More plots

\Figureref{figure:scatter-dds} shows the effects of adding Walsh's {DBLP:conf/ijcai/Walsh97}
depth-bounded discrepancy search (DDS) to \algorithmref{algorithm:sip}. Each point represents the solving
time for one instance---to avoid noise for easier instances, we measure only time spent during
search, and exclude time spent in preprocessing and initialisation.  Points below the $x-y$ diagonal
are speedups, whilst points on the top and right axes represent instances which timed out after one
thousand seconds with one algorithm, but not the other. For satisfiable instances, the different
point styles show the different families, whilst all unsatisfiable instances are shown as dark dots.

@@

@@

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-restarts.pdf}

    \caption{The cumulative number of satisfiable instances solved over time, with and without
    restarts.}
    \label{figure:restarts}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-random.pdf}
    \caption{Comparing basic backtracking with the degree heuristic, versus the random heuristic
    with restarts.}
    \label{figure:scatter-random}
\end{figure}

    \caption{Comparing basic backtracking with the degree heuristic, versus the biased
    heuristic with restarts.}
    \label{figure:scatter-by-family}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-mcs.pdf}
    \caption{The cumulative number of maximum common induced subgraph instances solved by
    k${\downarrow}$ and McSplit${\downarrow}$ over time, with and without restarts.}\label{figure:mcs}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-kdown.pdf}
    \caption{Comparing k${\downarrow}$ with and without restarts on an instance by instance basis.}\label{figure:kdown}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-mcsplit.pdf}
    \caption{Comparing McSplit${\downarrow}$ with and without restarts on an instance by instance
    basis.}\label{figure:mcsplit}
\end{figure}

>>>>

\Figureref{figure:scatter-dds} shows the effects of adding Walsh's \cite{DBLP:conf/ijcai/Walsh97}
depth-bounded discrepancy search (DDS) to \algorithmref{algorithm:sip}. Each point represents the solving
time for one instance---to avoid noise for easier instances, we measure only time spent during
search, and exclude time spent in preprocessing and initialisation.  Points below the $x-y$ diagonal
are speedups, whilst points on the top and right axes represent instances which timed out after one
thousand seconds with one algorithm, but not the other. For satisfiable instances, the different
point styles show the different families, whilst all unsatisfiable instances are shown as dark dots.

@@

\begin{figure}[tb]
    \centering
    \includegraphics*{gen-graph-restarts.pdf}

    \caption{The cumulative number of satisfiable instances solved over time, with and without
    restarts and nogood recording.}
    \label{figure:restarts}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-random-goods.pdf}
    \caption{Comparing basic backtracking with the degree heuristic, versus the random heuristic
    with restarts, but without nogood recording.}
    \label{figure:scatter-random-goods}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-random.pdf}
    \caption{Comparing basic backtracking with the degree heuristic, versus the random heuristic
    with restarts and nogood recording.}
    \label{figure:scatter-random}
\end{figure}

    \caption{Comparing basic backtracking with the degree heuristic, versus the biased
    heuristic with restarts and nogood recording.}
    \label{figure:scatter-by-family}
\end{figure}

@@

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-mcs.pdf}
    \caption{The cumulative number of maximum common induced subgraph instances solved by
    k${\downarrow}$ and McSplit${\downarrow}$ over time, with and without restarts and nogood
    recording.}\label{figure:mcs}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-kdown.pdf}
    \caption{Comparing k${\downarrow}$ with and without restarts and nogood recording on an instance
    by instance basis.}\label{figure:kdown}
\end{figure}

\begin{figure}[p]
    \centering
    \includegraphics*{gen-graph-scatter-mcsplit.pdf}
    \caption{Comparing McSplit${\downarrow}$ with and without restarts and nogood recording on an
    instance by instance basis.}\label{figure:mcsplit}
\end{figure}
